RNeXML: a package for reading and writing richly annotated phylogenetic, character, and trait data in R

### 2015-01-03 manuscripts/manuscript.Rmd
Fixes up the custom metadata section.

@@

>>>>

Metadata annotatuons in `NeXML` can be nested within another
annotation, which the `meta()` method accommodates by accepting a
parameter `children`, with the list of nested metadata objects (which
can themselves be nested) as value.

@@

Alternatively, additional namespaces can also be added in batch using
the `add_namespaces()` method, which makes a list of namespaces known
to a given `nexml` object (or created a new `nexml` object, similar to
other `add_*` methods).
